\documentclass[letterpaper, 11pt]{article}

\reversemarginpar
\usepackage{hyperref}
\usepackage{array}
\usepackage{fix-cm}
\usepackage[paper=letterpaper,
%includefoot, % Uncomment to put page number above margin
marginparwidth=0mm,    % Length of section titles
marginparsep=0.0mm,       % Space between titles and text
margin=25mm,              % 25mm margins
%lmargin=10mm,
%rmargin=10mm,            
%tmargin=6mm,
%bmargin=6mm,
includemp]{geometry}

\setlength{\parindent}{0in}

\usepackage[shortlabels]{enumitem}
\setcounter{secnumdepth}{-1}
% no page numbers 
\pagenumbering{gobble}
\begin{document}
	
	%\maketitle
	% Contact information will be right alligned, in footnote size
	\begin{center}
		\textbf{\Large Sharath Chandrashekhara}
	\end{center}
	
	\footnotesize
	\begin{center}
		University at Buffalo, Buffalo, NY\\
		sc296@buffalo.edu ${ | }$ \href{
			http://www.cse.buffalo.edu/~sc296}{\url{http://www.cse.buffalo.edu/~sc296}}
		\rule{\textwidth}{0.3mm}
	\end{center}
	
	\normalsize
	
	\subsection{Summary}
	\textbf{Computer Science Ph.D. Candidate} with close to 4 years of
	industrial experience in software research \& development. My research
	interests are \emph{Mobile Systems}, \emph{Cloud Storage} and
	\emph{Flash-based Storage}.
	
	\subsection{Education}
	\textbf{Ph.D. \hfill Aug `14 -- Present}\\
	I am a $3^{rd}$ year Ph.D. student in the Department of Computer Science and
	Engineering,
	University at Buffalo, advised by Dr.~Steven Ko. My current focus is on
	developing personalized storage on mobile platforms.
	\\
	
	\textbf{Master of Science\hfill Aug `12 -- Sept `14}\\
	I graduated from the Department of Computer Science and Engineering,
	University at Buffalo, with a specialization in \emph{Systems}. I was advised by
	Dr.~Steven Ko
	and Dr.~Vipin Choudhary in my Masters project.
	%CGPA: 3.84/4.00
	\\
	
	\textbf{Bachelor of Engineering\hfill Oct `05 --
		July `09}\\
	I graduated from Sri Jayachamarajendra College of Engineering (SJCE), Mysore,
	India,
	under the Visvesvaraya Technological University (VTU) securing a
	First Class with Distinction.
	
	\subsection{Research Projects and Publications}
	\begin{itemize}
		\item \textbf{BlueMountain} is a framework for flexible and personalized
		storage on mobile systems giving users higher control over their data.
		It is in active development and our preliminary work has been published in
		HotStorage 2015.\\
		\emph{``Enabling automated, rich, and versatile data management for
			android apps with BlueMountain.Chandrashekhara, S., Marcus, K.,
			Subramanya, R. G., Karve, H. S., Dantu, K., \& Ko, S. Y.,
			7th USENIX Workshop on Hot Topics in Storage and File Systems 2015.''}
		
		\item \textbf{Cider} is an erasure coded distributed block data store which I
		have developed with Dr.~Vipin Choudhary, to provide high flexibility in
		controlling data
		redundancy. We are working on extending this project to create a flexible
		flash based data archival system.\\
		\emph{Patent Pending, WO2015161140A1}
		
		\item \textbf{Pixelsior} is a photo management framework which can manage
		the photos on a device
		and can transparently manage content adaptation and image manipulation.
		Our initial work which was published in HotStorage 2016.\\
		\emph{``Pixelsior: Photo Management as a Platform Service for Mobile Apps
			Jeon, K., Chandrashekhara, S., Dantu, K., \& Ko, S. Y., 
			8th USENIX Workshop on Hot Topics in Storage and
			File Systems, 2016''}
		
		\item \textbf{PigOut} is a system that enables federated data processing over
		multiple Hadoop clusters. The work was published in IEEE Big Data
		conference.\\
		\emph{``Pigout: Making multiple hadoop clusters work
			together. In Big Data, 2014 IEEE International Conference. Jeon, K.,
			Chandrashekhara, S., Shen, F., Mehra, S.,
			Kennedy, O., \& Ko, S. Y.''}
		
	\end{itemize}
	
	\subsection{Teaching Experience}
	I have given guest lectures
	in grad level courses and have served as a teaching assistant for 5 terms.
	\begin{itemize}
		\item \textbf{Operating Systems: }Offered as CSE 421/521 by Dr. Tevfik Kosar
		--- Fall 2014 and 2015
		\item \textbf{Distributed Systems: }Offered as CSE 486/586 by Dr. Steve
			Ko ---
		Spring 2015, 2016 and 2017.
	\end{itemize}
	\subsection{Professional Experience}
	
	\textbf{SDE Summer Intern at Amazon Inc., Seattle \hfill Summer `13, `14,
		`15}\\
	I worked in the database engines team in the Amazon Web Services group and
	developed system modules for low-level database backup and restore, data
	compression and encryption in 
	Amazon Redshift --- Amazon's data warehouse service on the cloud.\\
	\\
	\textbf{Software Developer at NetApp Inc., Bangalore \hfill July `11 -- July
		`12}\\
	I worked on `Data-Ontap' --- NetApp's FreeBSD based operating system, for
	Enterprise Storage Controllers; on technologies like SCSI, Storage Area
	Networks
	(SAN), Network Attached Storage (NAS), RAID, Clustered Storage etc., with an
	exposure to development in the \textbf{Kernel Space and the Storage Stack}.\\
	
	\textbf{Software Engineer at NDS Ltd. (now a part of Cisco), Bangalore \hfill
		July `09 -- July `11}\\
	I worked on \emph{Digital TV Set Top Box} Middleware and related technologies
	like DVB/MPEG; in roles of Middleware debugging, device driver development and
	full stack integration. I also spent a brief stint working
	in the NDS R\&D Labs of Paris, France.
	
	%	\subsection{Technical Skill Set}
	%	\begin{itemize}
	%		\item Proficient in System Level C/C{}\verb!++! Programming with more
	%			than 3 years of experience in system software development. Familiar
	%			with Object Oriented Programming in higher level languages like
	%			Java, Python and Lisp.
	%		\item Have a good understanding of the various Network Protocols and
	%			familiar with Network programming.
	%		\item Have a good knowledge of the Hadoop platform and a working
	%			knowledge of the Android platform.
	%		\item Have basic GNU/Linux system administration skills and familiar
	%			with Bash scripting, Makefiles, \LaTeX, version control systems,
	%			SQL, various Linux command line tools etc., with a good
	%			understanding of the Software Development Cycle.
	%	\end{itemize}
	
	\subsection{Other Information}
	\begin{itemize}
		\item I am a homebrewer; a GNU/Linux and programming enthusiast.
		\item References available on request.
		\item Visa Status: F1-Student Visa, Citizenship: India. For further
		information please see my homepage or contact me.
	\end{itemize}
	\begin{center}
		\today{}
	\end{center}
	
\end{document}


